---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

body {
  background: lightblue;
}
h2 {
  color: red;
  font-family: "Lucida Console", "Courier New", monospace;
  font-weight: 700;
}
p {
  color: black;
  font-family: "Lucida Console", "Courier New", monospace;
}

```

## The report is tracking my number of steps and walking hours every day with question about steps ranges, hours walking, activities contributed most to my number of steps in the day, tracking dates and tracking methods.

```{r}
library(tidyverse)
csv_file <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vRWnCHH54zMXjApZ3AWLD5HP-F27-AL88Hd4FzOcmiFK8fPQfVwF6dQUml0-FrWEMjsdKAS8XAa7GL0/pub?gid=1032254020&single=true&output=csv"
logged_data <- read_csv(csv_file)

#rename variables in logged_data data frame
latest_data <- logged_data %>%
  rename(date_time_completing_survey  = 1,
         steps_range = 3,
         hours_walking = 4,
         activities = 5,
         actual_date = 6,
         tracking_methods = 7) 

#first actual date recorded
start_date <- latest_data$actual_date[1]

#last actual date recorded
last_date <- latest_data$actual_date[length(latest_data$actual_date)]

#number of responses
num_dates <- nrow(latest_data) 

```

The data was collected from `r start_date` to `r last_date` which was `r num_dates` days.


```{r}
#plot each variable
ggplot(data = latest_data) +
  geom_bar(aes(x = steps_range), fill="orange") +
  labs(title = "Steps ranges distribution")

less_than_1000 <- sum(grepl("< 1000", latest_data$steps_range, ignore.case = TRUE))

from_1000_to_4000 <- sum(grepl("1000 - 4000", latest_data$steps_range, ignore.case = TRUE))

from_4000_to_7000 <- sum(grepl("4000 - 7000", latest_data$steps_range, ignore.case = TRUE))

from_7000_to_10000 <- sum(grepl("7000 - 10000", latest_data$steps_range, ignore.case = TRUE))

more_than_10000 <- sum(grepl("> 10000", latest_data$steps_range, ignore.case = TRUE))

ranges <- c(
  "less than 1000" = less_than_1000,
  "1000 - 4000" = from_1000_to_4000,
  "4000 - 7000" = from_4000_to_7000,
  "7000 - 10000" = from_7000_to_10000,
  "more than 10000" = more_than_10000
)

most_frequent_range <- names(ranges)[which.max(ranges)]
most_frequent_count <- max(ranges)

least_frequent_range <- names(ranges)[which.min(ranges)]
least_frequent_count <- min(ranges)
```

Overall, I mostly walked `r most_frequent_range` steps per day that there were `r most_frequent_count` days of the range. There was only `r least_frequent_count` day that I walk `r least_frequent_range` steps.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = hours_walking), fill="blue") +
  labs(title = "Steps ranges distribution")

#maximum walking hours
maximum <- max(latest_data$hours_walking)

#minimum walking hours
minimum <- min(latest_data$hours_walking)

#average walking hours
average_walking_hours <- round(mean(latest_data$hours_walking), 1)
```

Over `r num_dates` days, I mostly walked 3 hours per day. The longest and shortest walking hours were `r maximum` and `r minimum` hours respectively and the average was `r average_walking_hours` hours.

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = activities), fill="green") +
  labs(title = "Steps ranges distribution")

# total number of dates that each activity contributed the most
uni_dates <- sum(grepl("Going to University", latest_data$activities, ignore.case = TRUE))
```

The activity that contributed the most to my steps number was going to university (`r uni_dates` days).

```{r}
#total numbers of date tracked by each method
smartphone_dates <- sum(grepl("smartphone", latest_data$tracking_methods, ignore.case = TRUE))

estimated_dates <- sum(grepl("estimated", latest_data$tracking_methods, ignore.case = TRUE))

smartwatch_dates <- sum(grepl("smartwatch", latest_data$tracking_methods, ignore.case = TRUE))

ggplot(data = latest_data) +
  geom_bar(aes(x = tracking_methods), fill="black") +
  labs(title = "Steps ranges distribution")

```

The steps range and approximate walking hours were mostly tracked by my smartphone which was `r smartphone_dates` days, and there was only `r estimated_dates` and `r smartwatch_dates` days that I tracked it by estimating and smartwatch respectively. 
